iSEE: Interactive SummarizedExperiment Explorer

### 2018-04-28 manuscript/main.tex
dynamic links

\subsection*{Dynamic linking between panels}
A key feature of iSEE is the ability to dynamically transmit information between panels (Fig.~\ref{fig:iSEE}B).
Users can define arbitrary links between ``transmitting'' and ``receiving'' panels, whereby selections in transmitting tables and plots highlight the corresponding data points in receiving panels.
This feature facilitates exploration of the relationships between different aspects of the data -- for example, users can easily determine co-expression patterns of genes in a particular region of a reduced dimensionality embedding, by transmitting information from the reduced dimension plot to one or more feature expression plots.
The linking paradigm extends to multiple plots whereby a plot can transmit to multiple receivers, or a receiving plot can itself transmit its own selection to another plot.
This allows users to mimic the arbitrarily complex gating strategies often found in analyses of flow cytometry data \citep{finak2014opencyto}, with the advantage of being extensible to any (meta)data present in a SummarizedExperiment object.
Information can similarly be transferred between tables and plots, e.g., selecting a row determines how points are coloured in receiving plots.

>>>>

\subsection*{Dynamic linking between panels}
A key feature of iSEE is the ability to dynamically transmit information between panels (Fig.~\ref{fig:iSEE}B).
Users can define and reorganize arbitrary links between ``transmitting'' and ``receiving'' panels, whereby selections in transmitting panels control the inclusion and appearance of the corresponding data points in receiving panels.
This feature facilitates exploration of the relationships between different aspects of the data.
For example, users can easily determine co-expression patterns of genes in a particular region of a reduced dimensionality embedding -- this is achieved by transmitting information from the reduced dimension plot to any number of feature expression plots.

Importantly, the linking paradigm extends to multiple panels, whereby a panel can transmit to multiple receivers, and a receiving panel can transmit its own selection to another plot.
Chains of linked plots allow users to mimic the arbitrarily complex gating strategies often found in analyses of flow cytometry data \citep{finak2014opencyto}.
Nevertheless, iSEE augments this functionality with the advantage of integrating filters based on any feature and column metadata present in a SummarizedExperiment object.
Lastly, both tables and plot panels may be used as sources and targets of dynamically linked selections (e.g., selecting a table row to control the coloring of data points in a plot).
